SU($n$) ferromagnets near the Heisenberg point

### 2021-04-22 collective_sun/sun_perturbation.tex
changed some formatting and revised intro

\documentclass[nofootinbib,notitlepage,11pt]{revtex4-2}

%%% linking references
\usepackage{hyperref}
\hypersetup{
  breaklinks=true,
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=cyan,
}

@@

SU($n$) symmetries play an important role in physics.  Underpinning
much of high energy physics, the celebrated SU($n$) gauge theory known
as Yang-Mills theory is central to our understanding of the
electroweak and strong forces.  Extensions of Yang-Mills and SU($n$)
symmetry feature in the most well-studied examples of holographic
duality\cite{maldacena1999largen} and the connection between
entanglement and gravity\cite{ryu2006holographic} through the anti-de
Sitter / conformal field theory (AdS/CFT) correspondence.  In a
condensed matter setting, SU(2) appears ubiquitously as a symmetry of
the Hubbard model, with important consequences for the study of
quantum magnetism and high temperature
superconductivity\cite{lee2006doping}.  The extension of the SU(2)
Hubbard model to SU($n$) has led to predictions of exotic phases of
matter such as valence bond solids\cite{read1989valencebond,
  rokhsar1990quadratic, kaul2012lattice, hermele2011topological} and
chiral spin liquids\cite{hermele2009mott, hermele2011topological,
  chen2016syntheticgaugefield, nataf2016chiral}, as well as the
potential to perform universal topological quantum
computation\cite{freedman2004class, nayak2008nonabelian}.
Furthermore, the consideration of disordered SU($n$) spin models has
opened analytically tractable avenues for studying quantum chaos and
information scrambling\cite{sachdev1993gapless,
  bentsen2019integrable}.

Last but not least, SU($n$) symmetries appear naturally in the physics
of atomic, molecular, and optical (AMO)
systems\cite{gorshkov2010twoorbital, beverland2016realizing,
  cazalilla2014ultracold, taie2012su, hofrichter2016direct,
  cappellini2014direct, scazza2014observation, zhang2014spectroscopic,
  goban2018emergence, perlin2019effective} through the independence of
atomic orbital and interaction parameters on the $n$ nuclear spin
states of individual atoms, with e.g.~$n=10$ in the case of
${}^{87}$Sr.  As a result, experiments can directly probe the SU($n$)
Hubbard model, leading to experimental observations of SU($n$) Hubbard
phases and phase transitions\cite{taie2012su, hofrichter2016direct},
two-orbital SU($n$) magnetism\cite{cappellini2014direct,
  scazza2014observation, zhang2014spectroscopic}, and multi-body
SU($n$)-symmetric interactions\cite{goban2018emergence,
  perlin2019effective}.  The tremendous theoretical significance of
SU($n$) symmetries makes it all the more exciting that they appear in
experimental platforms with exquisite degrees of microscopic control.
This control enables detailed studies of these symmetries'
consequences for fundamental questions in physics, as well as their
practical use in technological applications.  SU(2)-symmetric spin
interactions, for example, can play an important role in the
development of quantum sensors that make use of entanglement to
surpass classical limits on measurement
precision\cite{he2019engineering, perlin2020spin}.
The exciting prospect of similarly exploiting larger SU($n$)
symmetries to achieve a technological advantage is still an unexplored
avenue of research with enormous potential.

\red{[Paragraph on collective spin systems]}

@@

Before getting to the full SU($n$) Heisenberg model, we first revisit
the more common case of SU(2).  The SU(2) Heisenberg model consists of
$N$ two-level spins on a lattice, with spin-aligning interactions
\begin{align}
  H_0 = \sum_{i\ne j} h_{ij} \m s_i \c\m s_j,
  \label{eq:H_SU2}
\end{align}
where $i,j$ index individual spins; $h_{ij}$ are scalar coefficients
with $h_{ij}=h_{ji}$ and $h_{ii}=0$; and
$\m s_i\equiv\p{s_\x^{(i)},s_\y^{(i)},s_\z^{(i)}}$ is a vector of spin
operators $s_\alpha^{(i)}\equiv\sigma_\alpha^{(i)}/2$ defined by Pauli
operators $\sigma_\alpha^{(i)}$ acting on spin $i$.  In the standard
language of spin physics, each term of this Hamiltonian essentially
imposes an energy penalty of $-2h_{ij}$ to the formation of a spin 0
singlet state $\ket{\up\dn}-\ket{\dn\up}$ between spins $i$ and $j$,
favoring the formation of spin triplet states with total spin 1.
Another interpretation of the Hamiltonian in \eqref{eq:H_SU2} is
illuminated by the observation that the two-spin operator
$\m s_i\c\m s_j$ is, up to an overall constant, essentially the
two-qubit SWAP operation $\Pi_{ij}$.  We will refer to $\Pi_{ij}$ as
{\it permutation operator}, because its action on the Hilbert space
$\H\equiv\bigotimes_{k=1}^N\H_k$ of $N$ spins with individual Hilbert
spaces $\H_k$ is to permute the tensor factors of $\H$ associated with
spins $i$ and $j$ (see Figure \ref{fig:sketch_spins}).  Up to identity
terms with no physical consequence, we then have
\begin{align}
  H_0 = \sum_{i<j} h_{ij} \Pi_{ij},
  &&
  \Pi_{ij} \equiv \sum_{\mu,\nu} s_{\mu\nu}^{(i)} s_{\nu\mu}^{(j)}
  = \sum_{\mu,\nu} \op{\mu\nu}{\nu\mu}_{ij}
  \label{eq:H_0}
\end{align}
where $s_{\mu\nu}^{(i)}\equiv\op{\mu}{\nu}_i$ is a spin-transition
operator for spin $i$, and $\mu,\nu\in\set{\up,\dn}$ index the states
of a single spin.  In addition to providing a nice interpretation of
the Hamiltonian $H_0$ as essentially swapping the states of spins $i$
and $j$ at a rate $h_{ij}$, the definition of the SU(2)-symmetric
Heisenberg model in in \eqref{eq:H_0} is straightforward to generalize
to SU($n$) with arbitrary $n$.  That is, rather than having
$\mu,\nu\in\set{\up,\dn}$ index two spin states, we simply let
$\mu,\nu\in\set{1,2,\cdots,n}$ index the states (sometimes called {\it
  colors} or {\it flavors}) of an $n$-level spin.

\begin{figure}
  \centering
  \includegraphics[valign=m]{sketch_spins.pdf}
  $\stackrel{\displaystyle\Pi_{ij}}
  {\displaystyle\longleftrightarrow}$
  \includegraphics[valign=m]{sketch_spins_swap.pdf}
  \caption{The permutation operator $\Pi_{ij}$ swaps the states of
    interacting spins $i$ and $j$, which in the case of SU(2) can be
    represented by magnetization vectors in 3-dimensional space.  In
    the case of SU($n$), these vectors live in a higher-dimensional
    space without a clear geometric interpretation, but the
    interpretation of the permutation operator $\Pi_{ij}$ remains the
    same.}
  \label{fig:sketch_spins}
\end{figure}

@@

In the case of SU(2), the PS manifold $\M_0$ is precisely the {\it
  Dicke manifold} spanned by the PS states $\ket{m_\up,m_\dn}$ with a
definite (integer) number $m_\mu\ge0$ of spins occupying the
single-spin state $\mu\in\set{\up,\dn}$.  If there are $N$ spins
total, then Dicke states $\ket{m_\up,m_\dn}$ must have
$m_\up+m_\dn=N$.  In the case of multilevel spins, the PS manifold
$\M_0$ is similarly spanned by states
$\ket{m}=\ket{m_1,m_2,\cdots,m_n}$ with a definite occupation number
$m_\mu\ge0$ of the single-spin state $\mu$, and $\sum_\mu m_\mu=N$.
These states are essentially labeled by an assignment
$m=\p{m_1,m_2,\cdots,m_n}$ of $N$ (identical) spins to $n$ (distinct)
states.  We denote the set of all such assignments by $\A_n\p{N}$,
such that our standard basis for $\M_0$ is
$\set{\ket{m}:m\in\A_n\p{N}}$.  The dimension of $\M_0$, or
equivalently the ground-state degeneracy of $H_0$, is straightforward
to determine with a standard ``stars and bars'' calculation:
$\dim\p{\M_0}=\abs{\A_n\p{N}} = {N+n-1 \choose n-1} \sim N^{n-1}$.
The energy of any PS state $\ket\psi\in\M_0$ with respect to the
interaction Hamiltonian $H_0$ in \eqref{eq:H_0} is
\begin{align}
  E_0 = \sum_{i<j} h_{ij} = \f12 \sum_{i\ne j} h_{ij}.
\end{align}

@@

The sum in \eqref{eq:diagnosis_start} has terms with $i,j\notin k$,
terms with $i,j\in k$, and terms with only one of $i$ or $j\in k$.
The permutation operator $\Pi_{ij}$ acts trivially on $X_k\ket\psi$
when $i,j\notin k$, and we can replace the sum

@@

where $E_0 = \sum_{\set{i,j}\in\C_N\p{2}} h_{ij}$ is the interaction
energy of PS states $\ket\psi\in\M_0$, and

@@

with $k_a,k_b\in k\equiv\p{k_1,k_2,\cdots,k_M}$.  Defining a linear
operator $\hat{\m h}_{\t{D}}$ on the space of dimension-$M$ tensors,
whose action on $\m w$ is a new dimension-$M$ tensor with entries

@@

we can write the terms in \eqref{eq:diagnosis_start} with
$i,j\notin k$ as

@@

where $k_{a\lra b}$ denotes a list that is equal to
$k=\p{k_1,k_2,\cdots,k_M}$ but with $k_a$ and $k_b$ swapped, and we
have relabeled $k_a$ and $k_b$ to change $w_k X_{k_{a\lra b}}$ to
$w_{k_{a\lra b}} X_k$.  To write down these terms succinctly, we
define a linear operator $\hat{\m h}_{\t{P}}$ on the space of
dimension-$M$ tensors, whose action on $\m w$ is a new dimension-$M$
tensor with entries

@@

Finally, the terms in \eqref{eq:diagnosis_start} with only one of
$i\in k$ or $j\in k$ are

@@

where $k_{a:i}$ denotes a list that is equal to $k$ but with $k_a$
replaced by $i$, and we have relabeled $k_a$ and $i$ to change
$w_k X_{k_{a:i}}$ to $w_{k_{a:i}} X_k$.  For each fixed $a$, the sum
over $i$ above is essentially a contraction of the matrix $\m h$ with
the $a$-th index of the tensor $\m w$.  Defining a linear operator
$\hat{\m h}_a$ on the space of dimension-$M$ tensors, whose action on
$\m w$ is a new dimension-$M$ tensor with entries

@@

where $\m w_\Delta$ is the projection of $\m w$ onto the eigenspace of
$\hat{\m h}$ with eigenvalue $\Delta$, i.e.

@@

For reference, here $k_{a:i}$ is equal to
$k\equiv\p{k_1,k_2,\cdots,k_M}$ but with $k_a$ replaced by $i$;
$\C_M\p{2}$ is defined in \eqref{eq:choices}; $k_{a\lra b}$ is equal
to $k$ but with $k_a$ and $k_b$ swapped; and $h^{\t{D}}_k$ is defined
in \eqref{eq:multi_body_op_diag_element}.

@@

The set of all operators that are $\pm1$ on the diagonal is spanned by
sums and tensor products of the single-spin operators
$Z_\nu\equiv1-2\op\nu=\sum_{\mu\ne\nu}\op\mu-\op\nu$.  Given a list of
non-negative integers $z\equiv\p{z_1,z_2,\cdots,z_n}$ with
$\sum_\mu z_\mu=r$, we thus define the $r$-spin operator
\begin{align}
  X_z \equiv \bigotimes_\mu Z_\mu^{z_\mu},
\end{align}
and nominally use states of the form
$\ket{m,\m w,z}=\O\p{\m w,X_z}\ket{m}$ as our basis for the $r$-magnon
manifold $\M_r$.  There are three points to address concerning the
states $\ket{m,\m w,z}$:
\begin{enumerate*}
\item depending on the value of $m$, some choices of $z$ result in
  trivial states, $\ket{m,\m w,z}=0$;
  \label{pt:trivial}
\item the set of nontrivial states is generally overcomplete, in that
  any given state can be written as a nontrivial linear combination of
  others, and finally
  \label{pt:dependent}
\item even after identifying a linearly independent set of nontrivial
  states, any given pair of states $\ket{m,\m w,y},\ket{m,\m w,z}$
  with $y\ne z$ generally have a non-zero overlap, which is to say
  that they are not orthogonal.
  \label{pt:orthogonal}
\end{enumerate*}
To address the first two points, \ref{pt:trivial} and
\ref{pt:dependent}, we will place restrictions on the values of $z$
that we allow for any given $m$.  The last point, \ref{pt:orthogonal},
will require us to construct a basis of orthonormal states numerically
for any given values of $m,\m w$.

@@

% Here we simplify the single-body product
% \begin{align}
%   \O\p{\m u,X} \O\p{\m v,Y} \O\p{\m w,Z}
%   = \sum_{i,j,k} u_i v_j w_k X_i Y_j Z_k,
% \end{align}
% where $i,j,k$ index individual spins that the single-spin operators
% $X,Y,K$ act on; and $\m m\equiv\sum_i m_i\ket{i}$ for
% $\m m\in\set{\m u,\m v,\m w}$ are vectors of scalar coefficients.
% This product appears, for example, in the calculation of matrix
% elements of the operator $\O\p{\m v,Y}$ within the single-magnon
% manifold.  The diagrammatic expansion of this operator is
% \begin{multline}
%   \O\p{\m u,X} \O\p{\m v,Y} \O\p{\m w,Z}
%   \EQPS \diagram{prod_b111_c0} X_1 Y_2 Z_3
%   + \diagram{prod_b111_c10} X_1 Y_1 Z_1 \\
%   + \diagram{prod_b111_c11_u} X_1 Y_2 Z_2
%   + \diagram{prod_b111_c11_v} X_2 Y_1 Z_2
%   + \diagram{prod_b111_c11_w} X_2 Y_2 Z_1,
% \end{multline}
% where we can reduce (by hand or with a computer)

>>>>

\documentclass[nofootinbib,notitlepage,11pt]{revtex4-2}
\usepackage[T1]{fontenc}

%%% linking references
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
  breaklinks=true,
  colorlinks=true,
  allcolors=BlueViolet,
}

@@

SU($n$) symmetries play an important role in physics.
Underpinning much of high energy physics, the SU($n$) gauge theory known as Yang-Mills theory is central to our understanding of the electroweak and strong forces.
Extensions of Yang-Mills and SU($n$) symmetry feature in the most well-studied examples of holographic duality \cite{maldacena1999largen} and the connection between entanglement and gravity \cite{ryu2006holographic} through the anti-de Sitter/conformal field theory (AdS/CFT) correspondence.
In a condensed matter setting, SU($2$) appears ubiquitously as a symmetry of the Hubbard model, with important consequences for the study of quantum magnetism and high temperature superconductivity \cite{lee2006doping}.
The extension of SU($2$) Hubbard and spin models to SU($n$) has led to predictions of exotic phases of matter such as valence bond solids \cite{read1989valencebond, rokhsar1990quadratic, kaul2012lattice, hermele2011topological} and chiral spin liquids \cite{hermele2009mott, hermele2011topological, chen2016syntheticgaugefield, nataf2016chiral}, as well as the potential to perform universal topological quantum computation \cite{freedman2004class, nayak2008nonabelian} and other phenomena \cite{nataf2014exact, nataf2016exact}.
Furthermore, disordered SU($n$) spin models have opened analytically tractable avenues for studying quantum chaos and information scrambling \cite{sachdev1993gapless, bentsen2019integrable}.

The tremendous theoretical significance of SU($n$) symmetries makes it all the more exciting that they appear naturally in experimental atomic, molecular, and optical (AMO) platforms \cite{wu2003exact, cazalilla2009ultracold, gorshkov2010twoorbital, beverland2016realizing, cazalilla2014ultracold, taie2012su, hofrichter2016direct, cappellini2014direct, scazza2014observation, zhang2014spectroscopic, goban2018emergence, perlin2019effective} with exquisite degrees of microscopic control.
As a simple example, this symmetry arises through the independence of atomic orbital and interaction parameters on the $n$ nuclear spin states of alkaline-earth(-like) atoms, with e.g.~$n=10$ for ${}^{87}$Sr \cite{wu2003exact, cazalilla2009ultracold, cazalilla2014ultracold}.
As a result, AMO experiments can directly probe the role of SU($n$) interactions in controllable settings.
Recent progress includes the experimental observations of bosonization and faster thermalization in multi-component Fermi gas with SU($n$) symmetry \cite{song2020evidence, sonderhouse2020thermodynamics}, SU($n$) Hubbard phases and phase transitions \cite{taie2012su, hofrichter2016direct, taie2020observation}, two-orbital SU($n$) magnetism \cite{cappellini2014direct, scazza2014observation, zhang2014spectroscopic}, and multi-body SU($n$)-symmetric interactions \cite{goban2018emergence, perlin2019effective}.
In the spirit of quantum simulation, further investigations in controlled settings will play an important role in understanding the consequence of SU($n$) symmetries for fundamental questions in physics, as well as their practical use in technological applications.
For example, SU($2$)-symmetric spin interactions can be harnessed to develop quantum sensors that surpass classical limits on measurement precision \cite{he2019engineering, perlin2020spin}.
The prospect of similarly exploiting more general SU($n$) symmetries to achieve a technological advantage is still an unexplored avenue of research with untapped potential.

@@

Before getting to the full SU($n$) Heisenberg model, we first revisit
the more common case of SU(2).
The SU(2) Heisenberg model consists of
$N$ two-level spins on a lattice, with spin-aligning interactions
\begin{align}
  H_0 = \sum_{i\ne j} h_{ij} \m s_i \c\m s_j,
  \label{eq:H_SU2}
\end{align}
where $i,j$ index individual spins; $h_{ij}$ are scalar coefficients with $h_{ij}=h_{ji}$ and $h_{ii}=0$; and $\m s_i\equiv(s_\x^{(i)},s_\y^{(i)},s_\z^{(i)})$ is a vector of spin operators $s_\alpha^{(i)}\equiv\sigma_\alpha^{(i)}/2$ defined by Pauli operators $\sigma_\alpha^{(i)}$ acting on spin $i$.
In the standard language of spin physics, each term of this Hamiltonian essentially imposes an energy penalty of $-2h_{ij}$ to the formation of a spin 0 singlet state $\ket{\up\dn}-\ket{\dn\up}$ between spins $i$ and $j$, favoring the formation of spin triplet states with total spin 1.
Another interpretation of the Hamiltonian in \eqref{eq:H_SU2} is illuminated by the observation that the two-spin operator $\m s_i\c\m s_j$ is, up to an overall constant, essentially the two-qubit SWAP operation $\Pi_{ij}$.
We will refer to $\Pi_{ij}$ as {\it permutation operator}, because its action on the Hilbert space $\H\equiv\bigotimes_{k=1}^N\H_k$ of $N$ spins with individual Hilbert spaces $\H_k$ is to permute the tensor factors of $\H$ associated with spins $i$ and $j$ (see Figure \ref{fig:sketch_spins}).
Up to identity terms with no physical consequence, we then have
\begin{align}
  H_0 = \sum_{i<j} h_{ij} \Pi_{ij},
  &&
  \Pi_{ij} \equiv \sum_{\mu,\nu} s_{\mu\nu}^{(i)} s_{\nu\mu}^{(j)}
  = \sum_{\mu,\nu} \op{\mu\nu}{\nu\mu}_{ij}
  \label{eq:H_0}
\end{align}
where $s_{\mu\nu}^{(i)}\equiv\op{\mu}{\nu}_i$ is a spin-transition operator for spin $i$, and $\mu,\nu\in\set{\up,\dn}$ index the states of a single spin.
In addition to providing a nice interpretation of the Hamiltonian $H_0$ as essentially swapping the states of spins $i$ and $j$ at a rate $h_{ij}$, the definition of the SU(2)-symmetric Heisenberg model in in \eqref{eq:H_0} is straightforward to generalize to SU($n$) with arbitrary $n$.
That is, rather than having $\mu,\nu\in\set{\up,\dn}$ index two spin states, we simply let $\mu,\nu\in\set{1,2,\cdots,n}$ index the states (sometimes called {\it colors} or {\it flavors}) of an $n$-level spin.

\begin{figure}
  \centering \includegraphics[valign=m]{sketch_spins.pdf} $\stackrel{\displaystyle\Pi_{ij}} {\displaystyle\longleftrightarrow}$ \includegraphics[valign=m]{sketch_spins_swap.pdf}
  \caption{The permutation operator $\Pi_{ij}$ swaps the states of interacting spins $i$ and $j$, which in the case of SU(2) can be represented by magnetization vectors in 3-dimensional space.
    In the case of SU($n$), these vectors live in a higher-dimensional space without a clear geometric interpretation, but the interpretation of the permutation operator $\Pi_{ij}$ remains the same.
  }
\label{fig:sketch_spins}
\end{figure}

@@

In the case of SU(2), the PS manifold $\M_0$ is precisely the {\it Dicke manifold} spanned by the PS states $\ket{m_\up,m_\dn}$ with a definite (integer) number $m_\mu\ge0$ of spins occupying the single-spin state $\mu\in\set{\up,\dn}$.
If there are $N$ spins total, then Dicke states $\ket{m_\up,m_\dn}$ must have $m_\up+m_\dn=N$.
In the case of multilevel spins, the PS manifold $\M_0$ is similarly spanned by states $\ket{m}=\ket{m_1,m_2,\cdots,m_n}$ with a definite occupation number $m_\mu\ge0$ of the single-spin state $\mu$, and $\sum_\mu m_\mu=N$.

These states are essentially labeled by an assignment $m=\p{m_1,m_2,\cdots,m_n}$ of $N$ (identical) spins to $n$ (distinct) states.
We denote the set of all such assignments by $\A_n\p{N}$, such that our standard basis for $\M_0$ is $\set{\ket{m}:m\in\A_n\p{N}}$.
The dimension of $\M_0$, or equivalently the ground-state degeneracy of $H_0$, is straightforward to determine with a standard ``stars and bars'' calculation: $\dim\p{\M_0}=\abs{\A_n\p{N}} = {N+n-1 \choose n-1} \sim N^{n-1}$.
The energy of any PS state $\ket\psi\in\M_0$ with respect to the interaction Hamiltonian $H_0$ in \eqref{eq:H_0} is
\begin{align}
  E_0 = \sum_{i<j} h_{ij} = \f12 \sum_{i\ne j} h_{ij}.
\end{align}

@@

The sum in \eqref{eq:diagnosis_start} has terms with $i,j\notin k$, terms with $i,j\in k$, and terms with only one of $i$ or $j\in k$.
The permutation operator $\Pi_{ij}$ acts trivially on $X_k\ket\psi$ when $i,j\notin k$, and we can replace the sum

@@

where $E_0 = \sum_{\set{i,j}\in\C_N\p{2}} h_{ij}$ is the interaction energy of PS states $\ket\psi\in\M_0$, and

@@

with $k_a,k_b\in k\equiv\p{k_1,k_2,\cdots,k_M}$.
Defining a linear operator $\hat{\m h}_{\t{D}}$ on the space of dimension-$M$ tensors, whose action on $\m w$ is a new dimension-$M$ tensor with entries

@@

we can write the terms in \eqref{eq:diagnosis_start} with $i,j\notin k$ as

@@

where $k_{a\lra b}$ denotes a list that is equal to $k=\p{k_1,k_2,\cdots,k_M}$ but with $k_a$ and $k_b$ swapped, and we have relabeled $k_a$ and $k_b$ to change $w_k X_{k_{a\lra b}}$ to $w_{k_{a\lra b}} X_k$.
To write down these terms succinctly, we define a linear operator $\hat{\m h}_{\t{P}}$ on the space of dimension-$M$ tensors, whose action on $\m w$ is a new dimension-$M$ tensor with entries

@@

Finally, the terms in \eqref{eq:diagnosis_start} with only one of $i\in k$ or $j\in k$ are

@@

where $k_{a:i}$ denotes a list that is equal to $k$ but with $k_a$ replaced by $i$, and we have relabeled $k_a$ and $i$ to change $w_k X_{k_{a:i}}$ to $w_{k_{a:i}} X_k$.
For each fixed $a$, the sum over $i$ above is essentially a contraction of the matrix $\m h$ with the $a$-th index of the tensor $\m w$.
Defining a linear operator $\hat{\m h}_a$ on the space of dimension-$M$ tensors, whose action on $\m w$ is a new dimension-$M$ tensor with entries

@@

where $\m w_\Delta$ is the projection of $\m w$ onto the eigenspace of $\hat{\m h}$ with eigenvalue $\Delta$, i.e.

@@

For reference, here $k_{a:i}$ is equal to $k\equiv\p{k_1,k_2,\cdots,k_M}$ but with $k_a$ replaced by $i$; $\C_M\p{2}$ is defined in \eqref{eq:choices}; $k_{a\lra b}$ is equal to $k$ but with $k_a$ and $k_b$ swapped; and $h^{\t{D}}_k$ is defined in \eqref{eq:multi_body_op_diag_element}.

@@

The set of all operators that are $\pm1$ on the diagonal is spanned by sums and tensor products of the single-spin operators $Z_\nu\equiv1-2\op\nu=\sum_{\mu\ne\nu}\op\mu-\op\nu$.
Given a list of non-negative integers $z\equiv\p{z_1,z_2,\cdots,z_n}$ with $\sum_\mu z_\mu=r$, we thus define the $r$-spin operator
\begin{align}
  X_z \equiv \bigotimes_\mu Z_\mu^{z_\mu},
\end{align}
and nominally use states of the form $\ket{m,\m w,z}=\O\p{\m w,X_z}\ket{m}$ as our basis for the $r$-magnon manifold $\M_r$.
There are three points to address concerning the states $\ket{m,\m w,z}$:
\begin{enumerate*}
\item \label{pt:trivial} depending on the value of $m$, some choices of $z$ result in trivial states, $\ket{m,\m w,z}=0$;
\item \label{pt:dependent} the set of nontrivial states is generally overcomplete, in that any given state can be written as a nontrivial linear combination of others, and finally
\item \label{pt:orthogonal} even after identifying a linearly independent set of nontrivial states, any given pair of states $\ket{m,\m w,y},\ket{m,\m w,z}$ with $y\ne z$ generally have a non-zero overlap, which is to say that they are not orthogonal.
\end{enumerate*}
To address the first two points, \ref{pt:trivial} and \ref{pt:dependent}, we will place restrictions on the values of $z$ that we allow for any given $m$.
The last point, \ref{pt:orthogonal}, will require us to construct a basis of orthonormal states numerically for any given values of $m,\m w$.

@@

% Here we simplify the single-body product
% \begin{align}
%   \O\p{\m u,X} \O\p{\m v,Y} \O\p{\m w,Z}
%   = \sum_{i,j,k} u_i v_j w_k X_i Y_j Z_k,
% \end{align}
% where $i,j,k$ index individual spins that the single-spin operators $X,Y,K$ act on; and $\m m\equiv\sum_i m_i\ket{i}$ for $\m m\in\set{\m u,\m v,\m w}$ are vectors of scalar coefficients.
% This product appears, for example, in the calculation of matrix elements of the operator $\O\p{\m v,Y}$ within the single-magnon manifold.
% The diagrammatic expansion of this operator is
% \begin{multline}
%   \O\p{\m u,X} \O\p{\m v,Y} \O\p{\m w,Z}
%   \EQPS \diagram{prod_b111_c0} X_1 Y_2 Z_3
%   + \diagram{prod_b111_c10} X_1 Y_1 Z_1 \\
%   + \diagram{prod_b111_c11_u} X_1 Y_2 Z_2
%   + \diagram{prod_b111_c11_v} X_2 Y_1 Z_2
%   + \diagram{prod_b111_c11_w} X_2 Y_2 Z_1,
% \end{multline}
% where we can reduce (by hand or with a computer)
